\documentclass[12pt, glossary]{dalthesis}
%\usepackage[utf8]{inputenc}
\usepackage{graphicx}
%\usepackage{tgtermes} 
\graphicspath{ {images/} }
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{fancyvrb}
\usepackage{tikz}
\usepackage{tikz-qtree}
\usepackage{listings}
\usepackage{multicol}
\usepackage{amsthm}
\usepackage{amsmath }
\usepackage{xcolor}
\usepackage{framed}
\usepackage{color,soul}
\usepackage{tikz-cd}
\usetikzlibrary{matrix,arrows,decorations.pathmorphing, shadows, trees}
\usepackage{nomencl}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{enumerate}
%%
%% Maple definitions (c) 2008 Alexander Shapiro
%%
\lstdefinelanguage{Maple}
{keywords={and,assuming,break,by,catch,description,do,done, elif,else,end,error,export,fi,finally,for,from,global,if, implies,in,intersect,local,minus,mod,module,next,not,od,%
option,options,or,proc,quit,read,return,save,stop,subset,then, to,try,union,use,uses,while,xor},
sensitive=true,
morecomment=[l]\#,
morestring=[b]",
morestring=[d]"
}[keywords,comments,strings]

\definecolor{mygreen}{RGB}{34,139,34}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\lstset{ 
   xleftmargin=-25pt,
   xrightmargin=-25pt,
   framesep=0pt,
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}; should come as last argument
  basicstyle=\small,        % the size of the fonts that are used for the code
  breakatwhitespace=true,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
%  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygreen},    % comment style
%  deletekeywords={...},            % if you want to delete keywords from the given language
%  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
%  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
%  firstnumber=5,                % start line enumeration with line 1000
  frame=single,	                   % adds a frame around the code
  keepspaces=false,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=\bfseries\color{blue},       % keyword style
  language=Maple,                 % the language of the code
  morekeywords={*,...},            % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\color{black}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{mymauve},     % string literal style
  tabsize=2,	                   % sets default tabsize to 2 spaces
 % title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
}



\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem*{corollary*}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem*{proposition*}{Proposition}
\newtheorem{definition-proposition}{Definition-Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem*{lemma*}{Lemma}
\newtheorem{conjecture}{Conjecture}
\newtheorem*{conjecture*}{Conjecture}

\theoremstyle{definition}
\newtheorem{example}{Example}
\newtheorem{construction}{Construction}
\newtheorem{notation}{Notation}
\newtheorem*{notation*}{Notation}
\newtheorem{definition}{Definition}
\newtheorem*{definition*}{Definition}
\newtheorem{observation}{Observation}
\newtheorem*{observation*}{Observation}
\newtheorem{question}{Question}
\newtheorem*{question*}{Question}

\begin{document}

\title{Valuative Capacity of Some Compact Subsets of Ultrametric Spaces}
\author{Anne Johnson}

\mcs

\degree{Master of Science}
\degreeinitial{M.Sc.}
\faculty{Science}
\dept{Faculty of Mathematics}


% Month and Year of Defence
\defencemonth{August}\defenceyear{2019}

%\dedicate{Optionally, the thesis can be dedicated to someone, and the
%  student can enter the dedication content here.}

\nolistoftables
\nolistoffigures

\frontmatter


\begin{abstract}
In the course of developing a generalized factorial function, Manjul Bhargava introduced the notion of  $p-$orderings of a Dedekind domain \cite{mb1, mb2}, a combinatorial concept which, along with his generalized factorial, provided deep and perhaps unexpected results in number theory. In this thesis, we examine how a tool based on $p-$orderings can extend the concept of \textit{valuative capacity} from classical analysis to non-Archimedean settings.\\

When our space has algebraic structure, we show how this structure can be exploited to compute capacity. We then develop conditions for computing capacity in spaces that lack algebraic structure by studying the lattice of closed balls in the space. At the end of the thesis, we compute the capacity $n-$fold products of $(\mathbb{Z}, \rho_{p_i})$, for a set of $p-$adic metrics $p_i$. While this is a  straightforward process when using a fixed prime, we see that allowing distinct primes on each component produces interesting results even for $n=2$. We conjecture that these spaces have transcendental capacity.  \\

\end{abstract}

\printglossary

\begin{acknowledgements}
  First and foremost, I would like to thank my advisor, Dr. Keith Johnson, for several years of steady guidance and support. I would also like to thank Drs. Sara Faridi and Dorette Pronk for their mentorship over the years.\\
  
 Thanks to Daniele Turchetti for helpful feedback on work which unforunately came at too late an hour to be included here. Thanks as well to my readers, Drs. Karl Dilcher and Dorette Pronk, for their time and feedback.\\
 

 
\end{acknowledgements}

\mainmatter

\glossary{name={$\inf$},description={the infimum of a set}}
\glossary{name={$\sup$},description={the supremum of a set}}
\glossary{name={$\mu$},description={a Borel measure on $\mathbb{C}$}}
\glossary{name={$p$},description={a fixed prime}}
\glossary{name={$\mathbb{C}$},description={the complex numbers}}
\glossary{name={$\mathbb{R}$},description={the real numbers}}
\glossary{name={$\mathbb{Z}$},description={the integers}}
\glossary{name={$\mathbb{N}$},description={the natural numbers}}
\glossary{name={$\delta(n)$},description={the characteristic sequence of a set}}
\glossary{name={$\rho$},description={an ultrametric}}
\glossary{name={$\rho_N$},description={an ultrametric, induced by a norm N}}
\glossary{name={$v_p(z)$},description={the $p-$adic valuation of $z$}}
\glossary{name={$\lvert \cdot \rvert_p$},description={the $p$-adic absolute value}}
\glossary{name={$\rho_p$},description={the $p$-adic metric}}
\glossary{name={$\rho_\infty$},description={the max metric on a product space}}
\glossary{name={$B(x,r)$},description={the closed ball of radius $r$ centred at $x$}}
\glossary{name={$B^0(x,r)$},description={the open ball of radius $r$ centred at $x$}}
\glossary{name={$\widehat{\mathbb{Z}_p}$},description={the $p-$adic integers}}
\glossary{name={$S(x,r)$},description={the sphere of radius $r$ centred at $x$}}
\glossary{name={$\Gamma_S$},description={the decreasing sequence of distances in $S$}} 
\glossary{name={$\gamma_k$},description={the $k^{th}$ element of $\Gamma_S$}} 
\glossary{name={$\beta(n)$},description={the structure sequence of a set}}
\glossary{name={$\alpha(n)$},description={the semi-regular sequence of a set}}
\glossary{name={$B^k_i$},description={an element of $S_{\gamma_k}$}}
\glossary{name={$S_{\gamma_k}$},description={the finite partition of $S$ by closed balls of radius $k$}}
\glossary{name={$T_S$},description={the lattice of closed balls in  $S$}}



\chapter{Introduction}
\input{chapters/introduction_outline}
\chapter{Capacity and Ultrametric spaces}
\input{chapters/background}
\chapter{$\rho$-orderings and the structure of $S$}
\input{chapters/computing_orderings}
\chapter{The structure of $T_S$}
\input{chapters/semiregularity}
\chapter{Application: Product spaces of $\mathbb{Z}$}
\input{chapters/product_space}
%\input{chapters/update}
%\chapter*{nov_presentation}
%\input{nov_presentation/presentation}
%\chapter*{feb_presentation}
%\input{feb_presentation/presentation}

\begin{thebibliography}{9}
\bibitem[Ac]{na} N.L. Ackerman, Completeness in Generalized Ultrametric Spaces, \textit{$p$-Adic Numbers, Ultrametric Analysis, and Applications} \textbf{5(2)} (2013), 89-105.
\bibitem[Am]{amice} Y. Amice, Interpolation $p$-adique, \textit{Bull. Soc. Math. France} \textbf{92} (1964) 117-180.
\bibitem[BR]{rum} M. Baker and R Rumely, \textit{Potential Theory and Dynamics on the Berkovich
Projective Line}, Amer. Math. Soc., Providence, 2010.
\bibitem[B1]{mb2} M. Bhargava, $P$-orderings and polynomial functions on arbitrary subsets of Dedekind
rings, \textit{J. reine angew. Math.}, \textbf{490} (1997), 101-127.
\bibitem[B2]{mb1} M. Bhargava, The factorial function and generalizations, \textit{Am. Math. Monthly}
\textbf{107} (2000), 783-799.
\bibitem[B3]{mb3} M. Bhargava, On $P$-orderings, Rings of Integer Valued Polynomials and Ultrametric
Analysis, \textit{Journal of the Amer. Math. Soc.} \textbf{22(4)} (2009), 963-993.
\bibitem[Ca]{dgc}  D. Cantor, On an extension of the definition of transfinite diameter and some applications, \textit{J. reine angew. Math} \textbf{316} (1980), 160-207.  
\bibitem[Ch]{jlc} J.-L. Chabert, Generalized factorial ideals, \textit{Commutative algebra, Arab. J. Sci. Eng.
Sect. C} \textbf{26} (2001), 51-68.
\bibitem[CEF]{cef} J.-L.Chabert, S. Evrard, Y. Fares, Regular subsets of valued fields and Bhargava’s $v$-orderings, \textit{Math. Z.} \textbf{274} (2013) 263-290.
\bibitem[EF]{ef} S. Evrard and Y. Fares, $p$-adic subsets whose factorials satisfy a generalized Legendre
formula, \textit{London Math. Soc.}, \textbf{40} (2008), 37-50.
\bibitem[FP]{fp} Y. Fares, S. Petite, The valuative capacity of subshifts of finite type, \textit{J. Number Theory} \textbf{158}
(2016), 165-184.
%\bibitem[GV]{gvdp} Lothar Gerritzen and Marius van der Put, Schottky Groups and Mumford Curves.
\bibitem[F]{fek} M. Fekete, Uber die Verteilung der Wurzelen bei gewisser algebraiche Gleichun-
gen mit ganzzahligen Koeffizienten, \textit{Math. Zeits.} \textbf{17} (1923), 228-249.
\bibitem[J1]{kj} K. Johnson, $p$-orderings, Fekete $n-$tuples and capacity in ultrametric spaces (in preparation).
\bibitem[J2]{kj2} K. Johnson, Limits of characteristic sequences of integer-valued polynomials on
homogeneous sets, \textit{J. Number Theory} \textbf{129} (2009), 2933-2942.
\bibitem[M]{mun} J. Munkres, \textit{Topology}, Prentice Hall Inc., Upper Saddle River NJ, 2000.
\bibitem[Ra1]{rand} T. Ransford, \textit{Potential Theory in the Complex Plane}, Cambridge University Press, Cambridge, 1995.
\bibitem[Ra2]{rand2} T. Randsford, Computation of Logarithmic Capacity, \textit{Comp. Methods Function Theory} \textbf{10} (2010), 555-578.
\bibitem[Ro]{ar} A.M. Robert, \textit{A course in p-adic analysis}, Springer-Verlag, New York, 2000.
\bibitem[S]{sim} B. Simon, Equilibrium measures and capacities in spectral theory, \textit{Inverse Probl. Imaging} \textbf{1}:4 (2007), 713–772. 
\bibitem[W]{wer} J. Wermer, \textit{Potential Theory}, Springer Lecture Notes in Mathematics, \textbf{408}, Providence, 1981.
\end{thebibliography}

\appendix
\chapter{Maple Code}
\input{chapters/appendix}	

\end{document} 